---
title: "Data 607 Homework week 3"
author: "Sergio Ortega Cruz"
date: "September 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Week 3 assignment

Please deliver links to an R Markdown file (in GitHub and rpubs.com) with solutions to problems 3 and 4 from chapter 8 of Automated Data Collection in R.  Problem 9 is extra credit.  You may work in a small group, but please submit separately with names of all group participants in your submission.
Here is the referenced code for the introductory example in #3:

```{r dataraw}
library(stringr)
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
#Use the character class [:alpha:] to extract alphabetic characters
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
#View name
name
```

### Copy the introductory example. The vector name stores the extracted names.
R> name

[1] "Moe Syslak"    "Burns, C. Montgomery"  "Rev.Timothy Lovejoy"
[4] "Ned Flanders"  "Simpson, Homer"   "Dr. Julius Hibbert"

1.- Use tools of this chapter to rearrange the vector so that all the elements conform to the standard

first_name last_name

```{r rearrange}
rearrange_names <- str_split(name, ",")
rearrange_names

rearrange_names <- data.frame(rearrange_names)
rearrange_names

ln <- data.frame(rearrange_names[1,])
fn <- data.frame(rearrange_names[2, ])
rearrange_names <- ifelse(fn == ln, ln , rbind(fn, ln))
rearrange_names
```

2.- Construct a logical vector indicating wheter a character has a title (i.e., Rev and Dr)

```{r title}

title <- str_detect(name, "[[:alpha:]]{2,}\\.")
title
```

3.- Construct a logical vector indicating wheter a character has a second name

```{r second}
secondname <- str_detect(name, "[A-Z]\\.{1}")
secondname
```

### Describe the types of strings that conform to the following regular expressions and construct an example that is matched by regular expression.

1.-[0-9]+\\$

Matches numbers 0-9 zero or more times with a dollar sign following the string


```{r sect1}

example <- "6729$"  
regex = "[0-9]+\\$"
str_extract(example, regex)
```


2.-\\b[a-z{1,4}]\\b

Matches character a-z at least 1 time and at most 4 times with empty string at either edge of the word

```{r sect2}

example <- "abcd efgh"  
regex = "\\b[a-z]{1,4}\\b"
str_extract(example, regex)
```

3.-*?\\.txt$

Matches a string followed by .txt

```{r sect3}

example <- "abcd.txt"  
regex = ".*?\\.txt$"
str_extract(example, regex)
```

4.-\\d{2}/\\d{2}/\\d{4}

Matches dates with two digit month, two digit day, and four digit year sepreated by

```{r sect4}

example <- "01/17/19889"  
regex = "\\d{2}/\\d{2}/\\d{4}"
str_extract(example, regex)
```


5.-<(.+?)>.+?,/\\1>

Matches an HTML tag

```{r sect5}

example = "<Title>Sometext</head><body>Sometext</body>"
regex = "<(.+?)>.+?</\\1>" 
str_extract(example, regex) 

```


##The following code hides a secret message. Crack it with R and Regular expressions. Hint: Some of the characters are more revealing tha others!The code snippet is also available in the materials at www.r-datacollection.com.


```{r challenge}
extra_credit <-"clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
extra_credit

#Find all uppercase letters
str_extract_all(extra_credit, "[[:upper:]]")
```

INDEED!